Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-10-31 paper.tex
update

\subsection{Semantic matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$ calculated in the quality model in subSection \ref{qualityModel}. The advantage of semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.

The semantic matchmaking is achieved by utilising semantic annotation with OWL and OWL-S. In this paper, we use MECE ontologies \cite{bleul2008self}, which could be considered to be an alternative form of ontology for services. In ontology, semantics specifies the both concepts and individuals in the terms of classes and instances wherer semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services. The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals. The overall matching making process is demonstrated in Figure \ref{matchmaking}.

\subsection{Ontology-based Index Cache}
In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality and mark the input-parameter concepts with a set of services. The key idea of the index is to create a mapping from the output-related concepts to matched input-related services while considering different levels of match types. Furthermore, the repository size could also be reduced by considering users' predefined acceptable semantic matching quality, which eliminates the influence of low composition accuracy.  The service repository size is further reduced to the available output parameter concepts are input-relevant and more than the threshold.

>>>>

\subsection{Semantic matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$ calculated in the quality model in subSection \ref{qualityModel}. The purpose of semantic matchmaking quality is to find more component services that satisfies the quality of QoS.

The semantic matchmaking is typically achieved by utilising OWL2 and OWL-S. In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL, MECE is considered to be an alternative semantic annotation for WSDL. MECE defines the service-related inputs and outputs with parameter-related concepts. OWL-DL is a sublanguage of OWL from extension of RDF. which specifies semantic information of concepts involved in MECE. The overall matching making process is demonstrated in Figure \ref{matchmaking}.

\subsection{Ontology-based Index Cached Optimisation}
In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality and mark the input-parameter concepts with a set of services. The key idea of the index is to create a mapping from the output-related concepts to matched input-related services while considering different levels of match types. Furthermore, the repository size could also be reduced by considering users' predefined acceptable semantic matching quality, which eliminates the influence of low composition accuracy.  The service repository size is further reduced to the available output parameter concepts are input-relevant and more than the threshold $\alpha$.
